---
title: "Dictionary of Kina Rutul"
format: 
  html:
    page-layout: full
editor: source
css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
```

## How to use
You can **search** the information in all the columns given.

To see the full page for the word click on it in the column **Glossing Label**. It contains examples in Rutul and their translations to Russian and also some morphological information for the word (**Inflection** section). If the word is a *complex noun*, in **Inflection** there will be a link to the word, which is inflected in this complex noun. Same is for *complex verbs*.

The column **Russian** represents a list of meanings translated to Russian for each lexical entry, **English** does the same, but in English. **Orthography** shows the word written in cyrillic transcription. **Part of Speech** indicates the part of speech of the lexical entry, five are represented: *noun, verb, adjective, complex noun* and *complex verb*. **Glossing label** is shown for users that gloss the Kina Rutul texts.

<style>
  ol {
    padding: 0;
    margin: 0;
  }
</style>

## Dictionary
```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(DT)
library(glue)

li_if_not_empty <- function(val) {
  if (length(is.na(val)) > 1) return (toString(val));
  if (is.na(val)) {return ('')}
  else {return (glue('<li>{val}</li>'))}
}

data<-read_tsv("./data/rutul_dict.tsv", show_col_types = FALSE)
names(data)<-make.names(names(data))

mutate(data, 
       href = glue('<a href="words/{gsub(", ","-",lexeme_id)}.html">{lexeme_id}</a>')) %>% 
  mutate(meanings_rus = gsub("<li>NA</li>", "", 
                              glue('<ol>
                                      <li>{meaning_1_rus}</li>
                                      <li>{meaning_2_rus}</li>
                                      <li>{meaning_3_rus}</li>
                                      <li>{meaning_4_rus}</li>
                                    </ol>'))) %>%
  mutate(meanings_rus = gsub(regex("<ol>\\s*<li>([^<>]*)<\\/li>\\s*<\\/ol>"), "\\1", meanings_rus))  %>%
  mutate(meanings = gsub("<li>NA</li>", "", 
                          glue('<ol>
                                  <li>{meaning_1}</li>
                                  <li>{meaning_2}</li>
                                  <li>{meaning_3}</li>
                                  <li>{meaning_4}</li>
                                </ol>'))) %>%
  mutate(meanings = gsub(regex("<ol>\\s*<li>([^<>]*)<\\/li>\\s*<\\/ol>"), "\\1", meanings))  %>%
  select(href, No.stress, Orthography, meanings_rus, meanings, Part.of.Speech) %>% 
  datatable(filter = 'top', escape = FALSE, rownames = FALSE,
            colnames = c("Glossing Label", "Lexical entry", "Orthography", "Russian", "English", "Part of Speech"),
            options = list(pageLength = 10, dom = 'top', 
                           columnDefs = list(
                             list(orderable = FALSE, className = 'details-control', targets = 0))))
```
