---
title: "Dictionary of Kina Rutul"
format: 
  html:
    page-layout: full
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
```

This is the dictionary of the Rutul language (Lezgic < East-Caucasian; glottocode: rutu1240), spoken in the settlement of Kina (Russia, Dagestan Republic).

This dictionary was collected during the fieldwork in 2016-2023 of Linguistic convergence laboratory (HSE University). We are grateful for all the consultants who helped us in our work.

The dictionary contains 1200+ lexical entries of different parts of speech (nouns, verbs, etc.), list of meanings collected for these entries, exemplifying sentences and also some morphological information.

<button onclick="window.location.href='./dictionary.html';" style="color: #094fb6; background-color: #f8f9fa; border-radius: 4px; border: 2px solid lightgray; font-size: 20px; padding: 8px;">
  Browse the dictionary
</button>


## How to cite
Please refer to the dictionary as follows:

```{r}
library(RefManageR)
BibOptions(check.entries = FALSE, style = 'text', bib.style = 'authoryear')
article_citation <- BibEntry(bibtype = 'misc', 
 key='alekseevaetal2024',
 title='Dictionary of Kina Rutul',
 author='A. Alekseeva and N. Beklemishev and M. Daniel and N. Dobrushina and K. Filatov and A. Ivanova and T. Maisak and I. Osorgin',
 year='2024',
 publisher='Linguistic Convergence Laboratory, HSE University',
 address='Moscow',
 url='https://lingconlab.github.io/kina-rutul-dict/')
```

::: {.panel-tabset}
### Plain text
```{r, results = 'asis'}
print(article_citation, .opts = list(style = 'text'))
```
### BibTeX

```{r}
print(article_citation, .opts = list(style = 'Bibtex'))
```
:::